---
title: "Normative Prerequisites of Parenthood through the Lens of a Survey Experiment"
date: 10-24-2025
description: "A commented guide through analysing a survey experiment"
format: 
  html:
    self-contained: true
editor: source
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6*1.1,
  fig.retina = 3,
  dev = "ragg_png",
  fig.align = "center",
  out.width = "90%",
  collapse = TRUE
)

options(
  digits = 4,
  width = 300,
  dplyr.summarise.inform = FALSE
)
```

# Introduction

This document provides the complete script for the analysis of data collected in the Czech Republic in Autumn last year. It was a survey experiment attempting to measure the normative prerequisites of parenthood in the Czech Republic using a survey experiment. Respondents from an online panel convenience sample were asked to rate parental readiness of couples whose traits we varied randomly. This analysis identifies AMCEs (causal effects of varying the vignette characteristics) and aims to test various hypotheses about interactions between respondent characteristics and vignette components.

Further documentation and the data itself can be accessed from the author upon request. Outputs such as tables and plots are written to the `plots/` and `tables/` folders in the project directory.

## Ideas for future analyses

- Instead of making models for each response variable separately, join them all up into 1 index? The answers are highly correlated anyway, particularly q1 and q2, which use the same scale.
- Investigate the robustness of including respondents with repeated vignettes. Check whether they are the same respondents who then rated more vignettes or new ones.

# Setup

I load the necessary packages for analysis. Mainly tidyverse for overall functionality, haven for importing .SAV data, and lme4 with marginaleffects and broom to obtain interpretable model outputs.

```{r libraries}
#| message: false
#| warning: false

# core functionality
library(tidyverse)
library(haven)
library(janitor)
library(sjmisc)

# modelling and hypothesis testing
library(lme4)
library(pbkrtest)

# tidy model outputs and marginal effects
library(broom)
library(broom.mixed)
library(broom.helpers)
library(marginaleffects)

# plotting
library(ggforce)
library(patchwork)
library(extrafont)

# table creation
library(flextable)
library(kableExtra)
```

Next I set up the plot theme and the recoding scheme to transform Czech value labels to English ones. I am also using a non-native font called Jost, so be sure to download it from Google fonts if you are replicating this at home. The download link is inside the codeblock.

```{r plot-theme}
#| message: false
#| warning: false
#| code-fold: true

# loading fonts
loadfonts(device = "win")

# custom ggplot theme
# get font at https://fonts.google.com/specimen/Jost
theme_nice <- function() {
  theme_minimal(base_family = "Jost") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "Jost", face = "bold"),
          axis.title = element_text(family = "Jost Medium"),
          axis.title.x = element_text(hjust = 0),
          axis.title.y = element_text(hjust = 1),
          strip.text = element_text(family = "Jost", face = "bold",
                                    size = rel(0.75), hjust = 0),
          strip.background = element_rect(fill = "grey90", color = NA))
}

# Set default theme and font stuff
theme_set(theme_nice())
update_geom_defaults("text", list(family = "Jost", fontface = "plain"))
update_geom_defaults("label", list(family = "Jost", fontface = "plain"))

#Function for relabeling all the variable levels to english
plotting_variable_labs <- scale_y_discrete(
  labels = c("nejsou manželé a svatbu v tuto chvíli neplánují" = "aren't married",
             "Žena" = "woman",
             "Muž" = "man",
             "jsou manželé" = "are married",
             "mají v pronájmu" = "rent a flat",
             "pořídili si na hypotéku" = "mortgage of flat",
             "zdědili po babičce" = "inherited a flat",
             "nebyla dostupná školka" = "unavailable daycare",
             "byla dostupná školka" = "available daycare",
             "ještě na jeden rok" = "fixed term contract\nfor 1 more year",
             "smlouvu na dobu neurčitou" = "permanent contract",
             "58.500 Kč" = "58.500 czk",
             "39.000 Kč" = "39.000 czk",
             "19.500 Kč" = "19.500 czk"))

# Make a little lookup table for nicer feature labels
variable_lookup <- tribble(
  ~variable,    ~variable_nice,
  "vbyt",  "Housing",
  "vpar",  "Partnership status",
  "vskol_fix", "Availability of public daycare",
  "vpoh",  "Gender of vignette",
  "vzam",  "Employment stability",
  "vplat", "Income"
) |>  
  mutate(variable_nice = fct_inorder(variable_nice))
```

Finally, I load in the raw data. The file path is managed by `config.R` — place `original_data.sav` in the `data/` folder.

```{r data}
#| message: false
#| warning: false
#| code-fold: true

source("config.R")

# import data
parents_raw <- read_sav(file.path(data_path, "original_data.sav")) |>
  as_factor() |> 
  clean_names("snake") # removes all the capitalisation
```

# Data cleaning

Raw data is in a wide format - one respondent and their 6 vignette ratings per row. The analysis requires data in a long format - one vignette rating per row.

A sizable chunk of respondents rated vignettes due to a fault in the randomisation procedure. Nevertheless, I decided to keep them, since randomisation with replacement shouldn't violate any of the assumptions behind this analysis, hence they bolster the overall sample size. Technically they rated "new vignettes" that differed in assigned names, but all the substantive component levels remained the same. It is possible to filter them out by simply adding `filter(stej == 0)` to the pipe.

```{r data-cleaning}
#| message: false
#| warning: false
#| code-fold: true

# Adding vignette number indicator at the end of response vars
# instead of it being at the beginning
parents_long <- parents_raw |> 
  rename_with(~ case_when(
    startsWith(.x, "r1") ~ paste0(sub("^r1", "", .x), "1"),
    startsWith(.x, "r2") ~ paste0(sub("^r2", "", .x), "2"),
    startsWith(.x, "r3") ~ paste0(sub("^r3", "", .x), "3"),
    startsWith(.x, "r4") ~ paste0(sub("^r4", "", .x), "4"),
    startsWith(.x, "r5") ~ paste0(sub("^r5", "", .x), "5"),
    startsWith(.x, "r6") ~ paste0(sub("^r6", "", .x), "6"),
    TRUE ~ .x
  ))

# adding an underscore before the vignette number indicator for simpler pivoting
colnames(parents_long) <- gsub("(\\d)$", "_\\1", colnames(parents_long))

# removing all underscores except the final one
colnames(parents_long) <- ifelse(
  grepl("_", colnames(parents_long)) & str_count(colnames(parents_long), "_") > 1,
  sub("_", "", colnames(parents_long)), colnames(parents_long))

# actual pivot into long format
parents_long <- parents_long |> 
  pivot_longer(
    cols = !c("id", "status", "s_4", "s_5", "s_6", "s_7", "s_8", "sex", "age",
              "age_kat", "reg", "size", "edu", "ms",
              "pinc", "hinc", "xx_1", "xx_2", "xx_3", "xx_4", "xx_5", "stej"),
    names_to = c(".value", "vignette"),
    names_sep = "_",
    values_drop_na = TRUE
  ) |> 
  
  # recodes and relevelling
  mutate(
    # making the continuous response var continuous
    q1rec = case_when(
    q1 == "Zcela nepřipraven" ~ 0,
    q1 == "1" ~ 1,
    q1 == "2" ~ 2,
    q1 == "3" ~ 3,
    q1 == "4" ~ 4,
    q1 == "5" ~ 5,
    q1 == "6" ~ 6,
    q1 == "7" ~ 7,
    q1 == "8" ~ 8,
    q1 == "9" ~ 9,
    q1 == "Zcela připraven" ~ 10,
    TRUE ~ NA
    ),
    
    q2rec = case_when(
    q2 == "Velmi nepravděpodobné" ~ 0,
    q2 == "1" ~ 1,
    q2 == "2" ~ 2,
    q2 == "3" ~ 3,
    q2 == "4" ~ 4,
    q2 == "5" ~ 5,
    q2 == "6" ~ 6,
    q2 == "7" ~ 7,
    q2 == "8" ~ 8,
    q2 == "9" ~ 9,
    q2 == "Velmi pravděpodobné" ~ 10,
    TRUE ~ NA
    ),
    
    # creating a kids indicator
    parent = as.factor(if_else(s_5 > 0, "Yes", "No")),
    
    # recoding to english
    economic_activity = factor(case_when(
    s_8 == "Student/učeň" ~ "Economically inactive",
    s_8 == "Zaměstnanec" ~ "Economically active",
    s_8 == "Osoba samostatně výdělečně činná/podnikatel" ~ "Economically active",
    s_8 == "Nezaměstnaný" ~ "Unemployed",
    s_8 == "Starobní/invalidní důchodce" ~ "Economically inactive",
    s_8 == "Na rodičovské, mateřské nebo otcovské dovolené" ~ "Economically inactive",
    s_8 == "Jiná" ~ "Other"
    )),
    
    # recoding education (low - medium - high)
    edu_rec = factor(case_when(
    edu == "ZŠ" ~ "Bez maturity",
    .default = edu
    )),
    
    # relevelling the pay of the vignette
    vplat = factor(vplat, levels=c("58.500 Kč", "39.000 Kč", "19.500 Kč")),
    vplat = relevel(vplat, ref = "39.000 Kč")
  )
  
# Fixing factor levels of nursery availability - they were reversed

parents_long$vskol_fix <- 
  ifelse(parents_long$vskol == levels(parents_long$vskol)[1], 
                               levels(parents_long$vskol)[2], 
                               levels(parents_long$vskol)[1])

parents_long$vskol_fix <- factor(parents_long$vskol_fix)

# relocating some vars
parents_long <- parents_long |> 
  relocate(vskol_fix, .after = vskol)

# removing the raw file from the environment
rm(parents_raw)
```

# Descriptive analysis

## Table of descriptive statistics

```{r descriptive-stats}
#| warning: false
#| message: false
#| code-fold: true

# table for response variables
parents_long |>
  summarise(
    Mean = sprintf("%.2f", mean(q1rec, na.rm = TRUE)),
    SD = sprintf("%.2f", sd(q1rec, na.rm = TRUE)),
    Min = min(q1rec, na.rm = TRUE),
    Max = max(q1rec, na.rm = TRUE),
    Missing = sum(is.na(q1rec))/sum(!is.na(q1rec))
  ) |>
  mutate(Measure = "Question 1", .before = 1) |>
  bind_rows(
    parents_long |>
      summarise(
        Measure = "Question 2",
        Mean = sprintf("%.2f", mean(q2rec, na.rm = TRUE)),
        SD = sprintf("%.2f", sd(q2rec, na.rm = TRUE)),
        Min = min(q2rec, na.rm = TRUE),
        Max = max(q2rec, na.rm = TRUE),
        Missing = sum(is.na(q2rec))/sum(!is.na(q2rec))
      )
  ) |>
  kbl(format = "html", escape = FALSE, 
      caption = "Descriptive Statistics for Response Variables") |>
  kable_classic(full_width = FALSE, html_font = "Times New Roman") |>
  row_spec(0, bold = TRUE)
```

## Bar charts of counts of the answers to the response variables

Practically the same, ratings below 5 were rarely ever given. The only notable difference is that respondents never said that the couple was completely unprepared to have a child (never gave a rating of 0 to q1).

```{r kernel-density-plots}
#| fig-height: 4
#| fig-width: 6
#| message: false
#| warning: false
#| code-fold: true

ggplot(parents_long, aes(x = q1rec)) +
  geom_bar(fill = "gray80", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 1)) +
  coord_cartesian(xlim = c(0, 10)) +
  labs(x = "Q1 Response", y = "Counts", title = "Counts of responses to question 1") +
  theme_nice()

ggplot(parents_long, aes(x = q2rec)) +
  geom_bar(fill = "gray80", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 1)) +
  coord_cartesian(xlim = c(0, 10)) +
  labs(x = "Q2 Response", y = "Counts", title = "Counts of responses to question 2") +
  theme_nice()
```

## The 11 point scales

#### Questions:

1\. Do jaké míry jsou \[jméno muže/ženy\] a \[jméno ženy/muže\] připraveni stát se rodiči?

0 - Zcela nepřipraveni, …, 10 - Zcela připraveni, Nevím

2\. Jak pravděpodobné podle Vás je, že se \[jméno muže/ženy\] a \[jméno ženy/muže\] stanou v příštích 3 letech rodiči?

0 - Velmi nepravděpodobné, …, 10 – Velmi pravděpodobné, Nevím

# Modelling and hypothesis testing

## Models for "How ready are \[couple names\] to have children?"

All these models are mixed effects models with respondent level random intercepts. The dependent variable is the question above, rated on an 11 point scale. All the hypotheses about interactions were tested on this dependent variable.

```{r modelling-q1}
#| warning: false
#| message: false
#| code-fold: true

# just respondent random intercepts (for plotting)
m_q1 <- lmer(
  q1rec ~ vpoh + vpar + vbyt + vskol_fix + vzam + vplat
  + (1 | id), # respondent random intercepts
  data = parents_long
)

# base model - controlling for respondent level heterogeneity and respondent characteristics, forms the base of comparisons with models with interactions

m_base_mod <- lmer(
  q1rec ~ vpoh + vpar + vbyt + vskol_fix + vzam + vplat
  + parent + economic_activity + sex + edu_rec + s_4 + s_7 + size + reg + age_kat
  + (1 | id), # respondent random intercepts
  data = parents_long
)

# modelling the order effect

m_base_mod_order <- lmer(
  q1rec ~ vpoh + vpar + vbyt + vskol_fix + vzam + vplat
  + factor(vignette)
  + parent + economic_activity + sex + edu_rec + s_4 + s_7 + size + reg + age_kat
  + (1 | id), # respondent random intercepts
  data = parents_long
)

# interaction between gender of vignette and other components

m_interaction_woman <- lmer(
  q1rec ~ (vpar + vbyt + vskol_fix + vzam + vplat) * vpoh
  + parent + economic_activity + sex + edu_rec + s_4 + s_7 + size + reg + age_kat
  + (1 | id), # respondent random intercepts
  data = parents_long
)

# interaction between respondent sex and vignette components

m_interaction_r_sex <- lmer(
  q1rec ~ (vpar + vbyt + vskol_fix + vzam + vplat + vpoh) * sex
  + reg + economic_activity + edu_rec + s_4 + s_7 + size + parent + age_kat
  + (1 | id),
  data = parents_long
)

# interaction between respondent housing tenure and rating of vignette housing

m_interaction_r_housing <- lmer(
  q1rec ~ vpoh + vpar + vskol_fix + vzam + vplat
  + vbyt * s_7
  + factor(vignette)
  + parent + economic_activity + sex + edu_rec + s_4 + size + reg + age_kat
  + (1 | id), # respondent random intercepts
  data = parents_long
)

# by parenthood

m_interaction_r_parent <- lmer(
  q1rec ~ (vpoh + vpar + vbyt + vskol_fix + vzam + vplat) * parent
  + factor(vignette)
  + economic_activity + sex + edu_rec + s_4 + s_7 + size + reg + age_kat
  + (1 | id), # respondent random intercepts
  data = parents_long
)

# by level of income in vignette (excluding vignette gender)
m_interaction_income <- lmer(
  q1rec ~ (vpoh + vpar + vbyt + vskol_fix + vzam) * vplat
  + factor(vignette)
  + parent + economic_activity + sex + edu_rec + s_4 + s_7 + size + reg + age_kat
  + (1 | id), # respondent random intercepts
  data = parents_long
)
```

## Hypothesis tests for interactions

Since these are all random effects models, I need to use a Kenward-Rogers approximation of degrees of freedom to be able to evaluate the F-test.

```{r hypothesis-tests}
#| warning: false
#| message: false
#| code-fold: true

# insert models to be compared to the base
models <- c("m_base_mod_order", "m_interaction_woman", "m_interaction_income", "m_interaction_r_sex", "m_interaction_r_housing", "m_interaction_r_parent")

# loops through comparisons and assembles a table
model_contrasts <- 
  map(models, ~ tidy(KRmodcomp(get(.x), m_base_mod)) |> 
  mutate(model = .x)) |> 
  bind_rows() |> 
  mutate(across(where(is.numeric), ~ pmax(round(.x, 3), 0.001)))
```

## Models for "How likely are according to you \[couple names\] to become parents in the next 3 years?"

Just a simple additive mixed effects model with the second 11-point question. Used to construct the first plot.

```{r modelling-q2}
#| warning: false
#| message: false
#| code-fold: true

# just a basic one here (for plotting)
m_q2 <- lmer(
  q2rec ~ vpoh + vpar + vbyt + vskol_fix + vzam + vplat
  + (1 | id), # respondent random intercepts
  data = parents_long
)
```

# Plotting and interpretation

First I estimate AMCEs (causal estimand) of the additive models with all the components. Then I look at the marginal means of different vignette features (average response to vignettes that included that feature). In the second step I perform nested model comparisons using an F-test to test the statistical significance of various interactions. Finally I provide various plots for the model with interactions between vignette gender and other vignette features.

## AMCE plot for Q1 and Q2 from basic mixed effect model

### Data wrangling for the plot itself

I pull out the AMCEs from the models with the marginaleffects package. The code below includes a rather annoying procedure to add reference category row set to 0 for the coefficient plots. I also apply nicer variable and value labels from the lookup table.

```{r AMCE-plot-data-cleaning}
#| warning: false
#| message: false
#| code-fold: true

# Get population level predictions
m_q1_mfx <- avg_slopes(
  m_q1,
  re.form = NULL # include all random effects in predictions
)
m_q2_mfx <- avg_slopes(
  m_q2,
  re.form = NULL
)

# Extract all the right-hand side variables
rhs_vars <- all.vars(stats::update(lme4::nobars(formula(m_q1)), 0 ~ .))

# Make a data frame of all the levels of all the non-numeric things
model_variable_levels <- tibble(
  variable = rhs_vars
) |> 
  mutate(levels = map(variable, ~{
    x <- parents_long[[.x]]
    if (is.numeric(x)) {
      ""
    } else if (is.factor(x)) {
      levels(x)
    } else {
      sort(unique(x))
    }
  })) |> 
  unnest(levels) |> 
  mutate(term = paste0(variable,levels))

m_q1_mfx_result <- m_q1_mfx |> 
  separate_wider_delim(
    contrast,
    delim = " - ",
    names = c("variable_level", "reference_level")
  )

m_q2_mfx_result <- m_q2_mfx |> 
  separate_wider_delim(
    contrast,
    delim = " - ",
    names = c("variable_level", "reference_level")
  )

m_q1_plotting <- model_variable_levels |> 
  left_join(
    m_q1_mfx_result,
    by = join_by(variable == term, levels == variable_level)
  ) |> 
  # make these zero
  mutate(
    across(
      c(estimate, conf.low, conf.high),
      ~ ifelse(is.na(.x), 0, .x)
    )
  ) |> 
  left_join(variable_lookup, by = join_by(variable)) |> 
  mutate(across(c(levels, variable_nice), ~fct_inorder(.)))

m_q2_plotting <- model_variable_levels |> 
  left_join(
    m_q2_mfx_result,
    by = join_by(variable == term, levels == variable_level)
  ) |> 
  # make these zero
  mutate(
    across(
      c(estimate, conf.low, conf.high),
      ~ ifelse(is.na(.x), 0, .x)
    )
  ) |> 
  left_join(variable_lookup, by = join_by(variable)) |> 
  mutate(across(c(levels, variable_nice), ~fct_inorder(.)))

m_q1q2_plotting <- add_rows(m_q1_plotting, m_q2_plotting, id = "model") |> 
  mutate(model = as.factor(case_when(
    model == 1 ~ "How ready are they to have a child?",
    model == 2 ~ "How likely are they to have a child in the next 3 years?"
  )))

# unload the intermediate things from the environment
rm(m_q1_plotting)
rm(m_q1_mfx)
rm(m_q1_mfx_result)

rm(m_q2_plotting)
rm(m_q2_mfx)
rm(m_q2_mfx_result)
```

### Plotting

The plot below shows the coefficients of the 2 additive base models analysing the 11-point response scales.

```{r AMCE-plot}
#| warning: false
#| message: false
#| code-fold: true

m_q1q2_plotting |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(
    aes(x = estimate, y = levels, color = model)
  ) +
    geom_vline(xintercept = 0) +
    geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                    position = position_dodge(width = 0.5)) +
    labs(
      x = "Average change on an 11 point scale in comparison to\nreference category",
      y = NULL,
      color = "Dependent variable"
    ) +
    facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
    plotting_variable_labs +
    theme(legend.position = "top") +
    guides(color = guide_legend(
      title = "Dependent variable",
      ncol = 1,
      byrow = TRUE)) +
    scale_color_manual(
      values = c("turquoise", "coral"),  # Match your existing colors
      breaks = c(
        "How ready are they to have a child?",
        "How likely are they to have a child in the next 3 years?"))
```

Finally I export the created plot to the `plots/` folder.

```{r plot-export-additive}
#| warning: false
#| message: false
#| code-fold: true

# export
ggsave("q1_q2_additive_model_plot.png", bg = "white",
       width = 15, height = 17, units = "cm",
       path = output_plots)
```

## Marginal means plot for Q1 and Q2

### Data wrangling

```{r MM-plot-data-cleaning}
#| warning: false
#| message: false
#| code-fold: true

components <- c("vpoh", "vpar", "vbyt", "vskol_fix", "vzam", "vplat")

m_means_q1 <- map(components, ~ predictions(
  model = m_q1,
  by = c(.x),
  re.form = NULL
) |> 
  rename(levels = .x) |> 
  mutate(variable = .x)
) |> 
  bind_rows() |> 
  left_join(variable_lookup, by = join_by(variable))

m_means_q2 <- map(components, ~ predictions(
  model = m_q2,
  by = c(.x),
  re.form = NULL
) |> 
  rename(levels = .x) |> 
  mutate(variable = .x)
) |> 
  bind_rows() |> 
  left_join(variable_lookup, by = join_by(variable))

m_means_q1q2 <- add_rows(m_means_q1, m_means_q2, id = "model") |> 
  mutate(model = as.factor(case_when(
    model == 1 ~ "How ready are they to have a child?",
    model == 2 ~ "How likely are they to have a child in the next 3 years?"
  )))
```

### Plotting

```{r MM-plot}
#| warning: false
#| message: false
#| code-fold: true

m_means_q1q2 |> 
  
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(
    aes(x = estimate, y = levels, color = model)
  ) +
    geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                    position = position_dodge(width = 0.5)) +
    labs(
      x = "Marginal mean",
      y = NULL,
      title = "Marginal means",
      subtitle = "(score ranging from 0 to 10)"
    ) +
    facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
    plotting_variable_labs +
    theme(legend.position = "top") +
    guides(color = guide_legend(
      title = "Dependent variable",
      ncol = 1,
      byrow = TRUE)) +
    scale_color_manual(
      values = c("turquoise", "coral"),  # Match your existing colors
      breaks = c(
        "How ready are they to have a child?",
        "How likely are they to have a child in the next 3 years?"))
```

And finally again exporting the output to the `plots/` folder.

```{r plot-export-mm}
#| warning: false
#| message: false
#| code-fold: true

# export
ggsave("marginal_means_base.png", bg = "white",
       width = 15, height = 17.8, units = "cm",
       path = output_plots)
```

## Interaction hypothesis tests table

This code chunk should output an html table that will show you the results of the hypothesis tests

```{r html-table}
#| warning: false
#| message: false
#| code-fold: true

model_contrasts |> 
  mutate(
    model = gsub("m_", "", model),
    model = gsub("_", " ", model),
    model = tools::toTitleCase(model),
    stat = sprintf("%.2f", stat),
    ndf = as.integer(ndf),
    ddf = sprintf("%.2f", ddf),
    p.value = ifelse(p.value < .001, "<.001", sprintf("%.3f", p.value))
  ) |> 
  select(Model = model, F = stat, ndf = ndf, ddf = ddf, p = p.value) |>
  kbl(format = "html", escape = FALSE, caption = "Model Comparisons") |> 
  kable_classic(full_width = FALSE, html_font = "Times New Roman")  |> 
  row_spec(0, bold = TRUE)
```

The code chunk below creates a standard APA table as a word document exported to the `tables/` folder.

```{r table-interaction-tests-export-to-word}
#| warning: false
#| message: false
#| code-fold: true

model_contrasts |> 
  mutate(
    model = gsub("m_", "", model),
    model = gsub("_", " ", model),
    model = tools::toTitleCase(model),
    stat = sprintf("%.2f", stat),
    ndf = as.integer(ndf),
    ddf = sprintf("%.2f", ddf),
    p.value = ifelse(p.value < .001, "<.001", sprintf("%.3f", p.value))
  ) |> 
  select(Model = model, F = stat, ndf = ndf, ddf = ddf, p = p.value) |>
  flextable() |> 
  set_caption("Model Comparisons") |> 
  theme_apa() |> 
  autofit() |> 
  save_as_docx(path = paste0(output_tables, "/contrasts.docx"))
```

## AMCE plot for Q1 interaction between components and vignette sex

### Data wrangling

```{r data-wrangling-interaction-plot}
#| warning: false
#| message: false
#| code-fold: true

sex_mfx <- m_interaction_woman |>
  avg_slopes(
    variables = components,
    by = "vpoh",
    re.form = NULL
  ) |> 
  separate_wider_delim(
    contrast,
    delim = " - ",
    names = c("variable_level", "reference_level")
  )

m_interaction_woman_plotting <- model_variable_levels |> 
  left_join(
    sex_mfx,
    by = join_by(variable == term, levels == variable_level)
  ) |> 
  # Make these zero
  mutate(
    across(
      c(estimate, conf.low, conf.high),
      ~ ifelse(is.na(.x), 0, .x)
    )
  ) |> 
  left_join(variable_lookup, by = join_by(variable)) |> 
  mutate(across(c(levels, variable_nice), ~fct_inorder(.))) |>
  mutate(vpoh = case_when(
    is.na(reference_level) ~ "Muž",
    .default = vpoh
  )) |> 
  mutate(vpoh = case_when(
    vpoh == "Muž" ~ "Man",
    vpoh == "Žena" ~ "Woman"
  ))
```

### Plotting

```{r plot-interaction}
#| warning: false
#| message: false
#| code-fold: true

interaction_woman_plot <-
m_interaction_woman_plotting |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(
    aes(x = estimate, y = levels, color = vpoh)
  ) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5)) +
  labs(
    x = "Average change on an 11 point scale in comparison to\nreference category",
    y = NULL,
    color = "Gender of vignette"
  ) +
  scale_color_manual(values = c("turquoise", "coral")) +
  scale_x_continuous(breaks=seq(-1.5, 0.5, 0.5)) +
  coord_cartesian(xlim = c(-1.75, 0.75)) +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  plotting_variable_labs +
  theme(legend.position = "top")
```

In this block I export the result to the `plots/` folder.

```{r export-interaction-plot}
#| warning: false
#| message: false
#| code-fold: true

ggsave(plot = interaction_woman_plot,
       "q1_woman_interaction_AMCE.png", bg = "white",
       width = 15, height = 17.8, units = "cm",
       path = output_plots)
```

## AMCE plot for Q1 interaction between components and income

### Data wrangling

```{r data-wrangling-interaction-plot-income}
#| warning: false
#| message: false
#| code-fold: true

income_mfx <- m_interaction_income |>
  avg_slopes(
    variables = components,
    by = "vplat",
    re.form = NULL
  ) |> 
  separate_wider_delim(
    contrast,
    delim = " - ",
    names = c("variable_level", "reference_level")
  )

m_interaction_income_plotting <- model_variable_levels |> 
  left_join(
    income_mfx,
    by = join_by(variable == term, levels == variable_level)
  ) |> 
  # Make these zero
  mutate(
    across(
      c(estimate, conf.low, conf.high),
      ~ ifelse(is.na(.x), 0, .x)
    )
  ) |> 
  left_join(variable_lookup, by = join_by(variable)) |> 
  mutate(across(c(levels, variable_nice), ~fct_inorder(.))) |> 
  mutate(vplat = case_when(
    is.na(reference_level) ~ "39.000 Kč",
    .default = vplat
  ))
```

### Plotting

```{r plot-interaction-income}
#| warning: false
#| message: false
#| code-fold: true

interaction_income_plot <-
m_interaction_income_plotting |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(
    aes(x = estimate, y = levels, color = vplat)
  ) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5)) +
  labs(
    x = "Average change on an 11 point scale in comparison to\nreference category",
    y = NULL,
    color = "Income level"
  ) +
  scale_x_continuous(breaks=seq(-1.5, 0.5, 0.5)) +
  coord_cartesian(xlim = c(-1.75, 0.75)) +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  plotting_variable_labs +
  theme(legend.position = "top")

```

Export to `plots/`

```{r export-interaction-plot-income}
#| warning: false
#| message: false
#| code-fold: true

ggsave(plot = interaction_income_plot,
       "q1_income_interaction_AMCE.png", bg = "white",
       width = 15, height = 17.8, units = "cm",
       path = output_plots)
```

## Combining the interaction plots

The two interaction plots are combined side by side, sharing y-axis labels and a common axis title.

```{r patchwork}
#| warning: false
#| message: false
#| code-fold: true

combined_plot <- interaction_woman_plot + interaction_income_plot +
  plot_layout(axes = "collect_y", axis_titles = "collect") &
  labs(color = NULL)

combined_plot
```

```{r export-combined-plot}
#| warning: false
#| message: false
#| code-fold: true

ggsave(plot = combined_plot,
       "combined_interaction_AMCE.png", bg = "white",
       width = 25, height = 17, units = "cm",
       path = output_plots)
```