---
title: "[Presentation Title]"
subtitle: "[Subtitle]"
author: "Thomas Philip Heyes"
institute: "Department of Sociology, Faculty of Social Studies, Masaryk University"
email: "thomas.philip.heyes@mail.muni.cz"
date: "[Date]"
footer-author: "Thomas Philip Heyes"
footer-title: "[Short Title]"
format:
  muni-fss-revealjs:
    self-contained: true
execute:
  echo: false
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(ggforce)
library(patchwork)
library(extrafont)
library(kableExtra)

knitr::opts_chunk$set(dev = "ragg_png")

loadfonts(device = "win")
load("../data/plot_objects.RData")

theme_set(theme_nice())
update_geom_defaults("text", list(family = "Jost", fontface = "plain"))
update_geom_defaults("label", list(family = "Jost", fontface = "plain"))
```

## [Outline]

[Placeholder]

## [Motivation]

[Placeholder]

## [Research Questions and Hypotheses]

[Placeholder]

## [Study Design — Survey Experiment]

[Placeholder]

## [Sample]

[Placeholder]

## [Average Marginal Component Effects]

:::: {.cols-3-7}

::: {}
[Key findings]

- [Component A]
- [Component B]
- [Component C]
:::

::: {}
```{r amce-plot}
#| fig-height: 5.5
#| fig-width: 4

m_q1q2_plotting |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(aes(x = estimate, y = levels, color = model)) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5)) +
  labs(x = "Average change on an 11 point scale\nin comparison to reference category",
       y = NULL, color = "Dependent variable") +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  plotting_variable_labs +
  theme(legend.position = "top") +
  guides(color = guide_legend(title = "Dependent variable", ncol = 1, byrow = TRUE)) +
  scale_color_manual(
    values = c("turquoise", "coral"),
    breaks = c("How ready are they to have a child?",
               "How likely are they to have a child in the next 3 years?"))
```
:::

::::

## [Marginal Means]

:::: {.cols-3-7}

::: {}
[Key findings]

- [Component A]
- [Component B]
- [Component C]
:::

::: {}
```{r mm-plot}
#| fig-height: 5.5
#| fig-width: 4

m_means_q1q2 |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(aes(x = estimate, y = levels, color = model)) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5)) +
  labs(x = "Marginal mean (0–10 scale)", y = NULL) +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  plotting_variable_labs +
  theme(legend.position = "top") +
  guides(color = guide_legend(title = "Dependent variable", ncol = 1, byrow = TRUE)) +
  scale_color_manual(
    values = c("turquoise", "coral"),
    breaks = c("How ready are they to have a child?",
               "How likely are they to have a child in the next 3 years?"))
```
:::

::::

## [Interaction Hypothesis Tests]

```{r interaction-table}
model_contrasts |>
  mutate(
    model = gsub("m_", "", model),
    model = gsub("_", " ", model),
    model = tools::toTitleCase(model),
    stat = sprintf("%.2f", stat),
    ndf = as.integer(ndf),
    ddf = sprintf("%.2f", ddf),
    p.value = ifelse(p.value < .001, "<.001", sprintf("%.3f", p.value))
  ) |>
  select(Model = model, F = stat, ndf, ddf, p = p.value) |>
  kbl(format = "html", escape = FALSE) |>
  kable_classic(full_width = FALSE, html_font = "Times New Roman") |>
  row_spec(0, bold = TRUE)
```

## [Interaction with Vignette Gender]

:::: {.cols-3-7}

::: {}
[Key findings]

- [Finding A]
- [Finding B]
:::

::: {}
```{r interaction-woman-plot}
#| fig-height: 6
#| fig-width: 5

m_interaction_woman_plotting |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(aes(x = estimate, y = levels, color = vpoh)) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5)) +
  labs(x = "Average change on an 11 point scale\nin comparison to reference category",
       y = NULL, color = "Gender of vignette") +
  scale_color_manual(values = c("turquoise", "coral")) +
  scale_x_continuous(breaks = seq(-1.5, 0.5, 0.5)) +
  coord_cartesian(xlim = c(-1.75, 0.75)) +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  plotting_variable_labs +
  theme(legend.position = "top")
```
:::

::::

## [Interaction with Income Level]

```{r combined-interaction-plot}
#| fig-height: 5.5
#| fig-width: 8
#| fig-align: center

interaction_woman_plot <- m_interaction_woman_plotting |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(aes(x = estimate, y = levels, color = vpoh)) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5)) +
  labs(x = "Average change on an 11 point scale\nin comparison to reference category",
       y = NULL, color = "Gender of vignette") +
  scale_color_manual(values = c("turquoise", "coral")) +
  scale_x_continuous(breaks = seq(-1.5, 0.5, 0.5)) +
  coord_cartesian(xlim = c(-1.75, 0.75)) +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  plotting_variable_labs +
  theme(legend.position = "top")

interaction_income_plot <- m_interaction_income_plotting |>
  mutate(levels = fct_relevel(levels, "19.500 Kč", "39.000 Kč", "58.500 Kč")) |>
  ggplot(aes(x = estimate, y = levels, color = vplat)) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5)) +
  labs(x = "Average change on an 11 point scale\nin comparison to reference category",
       y = NULL, color = "Income level") +
  scale_x_continuous(breaks = seq(-1.5, 0.5, 0.5)) +
  coord_cartesian(xlim = c(-1.75, 0.75)) +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  plotting_variable_labs +
  theme(legend.position = "top")

interaction_woman_plot + interaction_income_plot +
  plot_layout(axes = "collect_y", axis_titles = "collect") &
  labs(color = NULL)
```

## [Discussion]

[Placeholder]

## [Conclusions]

[Placeholder]

## Thank you

:::: {.cols-2}

::: {}
**Thomas Philip Heyes**

Department of Sociology
Faculty of Social Studies
Masaryk University
Joštova 10, Brno

thomas.philip.heyes@mail.muni.cz
:::

::: {}
{{< fa brands orcid >}} [0009-0001-3816-3425](https://orcid.org/0009-0001-3816-3425)

{{< fa brands bluesky >}} [thomasphilipheyes.bsky.social](https://bsky.app/profile/thomasphilipheyes.bsky.social)

{{< fa brands github >}} [ClangerThom](https://github.com/ClangerThom)

{{< fa brands linkedin >}} [thomas-philip-heyes](https://www.linkedin.com/in/thomas-philip-heyes-194079390/)

:::

::::

::: {.outro}
:::
